---
title: "HW10"
output:
  pdf_document:
    fig_height: 3.5
---

Bonus1

```{r}
##p=10
wrapper.function <- function(n.trials2) {
  eigen.value <- NULL
  for (i in 1:n.trials2) {
    data <- rmvnorm(n, sigma = covMatrix)
    covMatrix.est <- cov(data)
    eigen.value[[i]] <- max(eigen(covMatrix.est)$values)
  }
  list(eigen.value = eigen.value)
}
library(snow)
library(rlecuyer)
p <- 10
n <- 1000
covMatrix <- diag(p)
cl <- makeCluster(2, type = "SOCK")
clusterEvalQ(cl, library(mvtnorm))
clusterSetupRNG(cl, type = "RNGstream", seed = 10)
clusterExport(cl, list("covMatrix", "n"))
parRet <- clusterApply(cl, rep(200/2, 2), wrapper.function)
stopCluster(cl)
max.eigen.value <- unlist(parRet)
par(mfrow=c(1,2))
plot(max.eigen.value)
hist(max.eigen.value)
##p=50
wrapper.function <- function(n.trials2) {
  eigen.value <- NULL
  for (i in 1:n.trials2) {
    data <- rmvnorm(n, sigma = covMatrix)
    covMatrix.est <- cov(data)
    eigen.value[[i]] <- max(eigen(covMatrix.est)$values)
  }
  list(eigen.value = eigen.value)
}
library(snow)
library(rlecuyer)
p <- 50
n <- 1000
covMatrix <- diag(p)
cl <- makeCluster(2, type = "SOCK")
clusterEvalQ(cl, library(mvtnorm))
clusterSetupRNG(cl, type = "RNGstream", seed = 10)
clusterExport(cl, list("covMatrix", "n"))
parRet <- clusterApply(cl, rep(200/2, 2), wrapper.function)
stopCluster(cl)
max.eigen.value <- unlist(parRet)
par(mfrow=c(1,2))
plot(max.eigen.value)
hist(max.eigen.value)
##p=200
wrapper.function <- function(n.trials2) {
  eigen.value <- NULL
  for (i in 1:n.trials2) {
    data <- rmvnorm(n, sigma = covMatrix)
    covMatrix.est <- cov(data)
    eigen.value[[i]] <- max(eigen(covMatrix.est)$values)
  }
  list(eigen.value = eigen.value)
}
library(snow)
library(rlecuyer)
p <- 200
n <- 1000
covMatrix <- diag(p)
cl <- makeCluster(2, type = "SOCK")
clusterEvalQ(cl, library(mvtnorm))
clusterSetupRNG(cl, type = "RNGstream", seed = 10)
clusterExport(cl, list("covMatrix", "n"))
parRet <- clusterApply(cl, rep(200/2, 2), wrapper.function)
stopCluster(cl)
max.eigen.value <- unlist(parRet)
par(mfrow=c(1,2))
plot(max.eigen.value)
hist(max.eigen.value)
##p=800
wrapper.function <- function(n.trials2) {
  eigen.value <- NULL
  for (i in 1:n.trials2) {
    data <- rmvnorm(n, sigma = covMatrix)
    covMatrix.est <- cov(data)
    eigen.value[[i]] <- max(eigen(covMatrix.est)$values)
  }
  list(eigen.value = eigen.value)
}
library(snow)
library(rlecuyer)
p <- 800
n <- 1000
covMatrix <- diag(p)
cl <- makeCluster(2, type = "SOCK")
clusterEvalQ(cl, library(mvtnorm))
clusterSetupRNG(cl, type = "RNGstream", seed = 10)
clusterExport(cl, list("covMatrix", "n"))
parRet <- clusterApply(cl, rep(200/2, 2), wrapper.function)
stopCluster(cl)
max.eigen.value <- unlist(parRet)
par(mfrow=c(1,2))
plot(max.eigen.value)
hist(max.eigen.value)
```

COMMENT: We can see that the largest eigenvalue is getting larger as p increases.

Bonus2

```{r}
Rsquare <- function(flag, n) {
  ind <- seq(1, 1000, by=1)
  y.var <- rnorm(n)
  x.var <- matrix(NA, nrow=n, ncol=1000)
  x.var <- apply(x.var, 2, rnorm)
  x.cov <- sample(ind, 10, replace=FALSE)
  model <- lm(y.var ~ x.var[ , x.cov])
  r2 <- summary(model)$r.squared
}
n.trial <- 50000
r2.vec <- rep(NA, n.trial)
n <- 30
cl <- makeCluster(2, type = "SOCK")
r2.vec <- unlist(parLapply(cl, rep(1, n.trial), Rsquare, n=n))
stopCluster(cl)
(max.r2 <- max(r2.vec))
```

COMMENT: Because the largest value of R^2 is high enough, we can trust R^2.

Bonus3

COMMENT: Two well developed R packages stand out for use in high performance multicomputer environments: Rmpi ans snow. Both have acceptable usability, support a spectrum of functionality for parallel computing with R, and deliver good performance. However, packages for grid computing are still in development, with only one package currently available to the end user. For multi-core systems , five different pacakages exist, but a number of issues pose challenges to early adopters.
