---
title: "HW4"
output:
  pdf_document:
    fig_height: 3.5
---

Page40_Exercise3

(a)

```{r}
plot(pressure$pressure~pressure$temperature)
abline(lm(pressure$pressure~pressure$temperature),lty=1)
cor(pressure)
```

COMMENT: pressure and temperature seem to have nonlinear relationship.

(b)

```{r}
plot(pressure$pressure~pressure$temperature)
abline(lm(pressure$pressure~pressure$temperature),lty=1)
lines(pressure$temperature,(0.168+0.007*pressure$temperature)^(20/3),lty=2)
residuals<-with(pressure,pressure-(0.168+0.007*temperature)^(20/3))
qqnorm(residuals)
qqline(residuals)
```

COMMENT: Residuals seem to follow a skewed distribution.

(c)

```{r}
pressure$pressure2=pressure$pressure^(3/20)
plot(pressure$pressure2~pressure$temperature)
abline(lm(pressure$pressure2~pressure$temperature),lty=1)
fit<-lm(pressure$pressure2~pressure$temperature)
summary(fit)
```

COMMENT: After the power transformation, pressure2 and temperature have linear relationship.

(d)

```{r}
residuals2<-with(pressure,pressure2-(0.168+0.007*temperature))
qqnorm(residuals2)
qqline(residuals2)
```

COMMENT: After the power transformation, Residuals follow a normal distribution.

Page46_Exercise1

(a)

```{r}
#draw a histogram of log(islands,10) using the "Scott" rule without axes
hist(log(islands,10),breaks="Scott",axes=FALSE,xlab="area",main="Histogram of Island Areas")
#draw x coordinate according to the range of log(islands,10)
axis(1,at=1:5,labels=10^(1:5))
#draw y coordinate
axis(2)
#draw a box around a plot
box()
```

(b)

```{r}
hist(log(islands,10),breaks="Scott",axes=FALSE,xlab="area",main="Histogram of Island Areas",sub="Base-10Log-Scale.")
axis(1,at=1:5,labels=10^(1:5))
axis(2)
box()
```

(c)

```{r}
hist(round(log(islands,10)),breaks="Sturges",axes=FALSE,xlab="area",main="Histogram of Island Areas")
axis(1,at=0.5*(1:8)+0.5,labels=round(10^(0.5*(1:8)+0.5)))
axis(2)
box()
```

Page46_Exercise2

```{r}
plot(pressure$pressure~pressure$temperature)
curve((0.168+0.007*x)^(20/3),from=0,to=400,add=TRUE)
```

(b)

```{r}
pressure$pressure2=pressure$pressure^(3/20)
plot(pressure$pressure2~pressure$temperature)
abline(a=0.168,b=0.007,lty=1)
```

COMMENT: After the power transformation, pressure2 and temperature have linear relationship.

(c)

```{r}
plot(pressure$pressure2~pressure$temperature,main="Power Transformation")
abline(a=0.168,b=0.007,lty=1)
```

(d)

```{r}
pdf(file='graph1.pdf')
par(mfrow=c(1,2))
plot(pressure$pressure~pressure$temperature)
curve((0.168+0.007*x)^(20/3),from=0,to=400,add=TRUE)
plot(pressure$pressure2~pressure$temperature,main="Power Transformation")
abline(a=0.168,b=0.007,lty=1)
dev.off()
pdf(file='graph2.pdf')
par(mfrow=c(2,1))
plot(pressure$pressure~pressure$temperature)
curve((0.168+0.007*x)^(20/3),from=0,to=400,add=TRUE)
plot(pressure$pressure2~pressure$temperature,main="Power Transformation")
abline(a=0.168,b=0.007,lty=1)
dev.off()
```

