---
title: "HW5"
output:
  pdf_document:
    fig_height: 3.5
---

Page49_Exercise2

```{r}
Fibonacci<-numeric(31)
Fibonacci[1]<-1
Fibonacci[2]<-1
for (i in 3:31) Fibonacci[i]<-Fibonacci[i-2]+Fibonacci[i-1]
Fibonacci
ratio_seq<-numeric(30)
for (i in 1:30) ratio_seq[i]<-Fibonacci[i+1]/Fibonacci[i]
ratio_seq
golden_ratio<-(1+sqrt(5))/2
golden_ratio
```

COMMENT: the sequence of ratio of successive Fibonacci numbers converges to the golden ratio. Please see the appendix for proof.

Page49_Exercise3

```{r}
##a
answer<-0
for (j in 1:5) answer<-answer+j
answer
##b
answer<-NULL
for (j in 1:5) answer<-c(answer,j)
answer
##c
answer<-0
for (j in 1:5) answer<-c(answer,j)
answer
##d
answer<-1
for (j in 1:5) answer<-answer*j
answer
##e
answer<-3
for (j in 1:15) answer<-c(answer,(7*answer[j]%%31))
answer
```

COMMENT: 
1st=3
2nd=7*(3%%31)=21
3rd=7*(21%%31)=147
4th=7*(147%%31)=161
5th=7*(161%%31)=42
...
16th=7*(182%%31)=189

Page50_Exercise6

```{r}
##a
###x<-0.5
###count<-0
###while(abs(x-1.5*cos(x))>0.000001){
###  x<-1.5*cos(x)
###  count<-count+1
###}
###x
###count
x<-0.5
count<-0
while(abs(x-cos(x)/30-44*x/45)>0.000001){
  x<-cos(x)/30+44*x/45
  count<-count+1
}
x
count
##c
abs(-1.5*sin(x))
abs(-sin(x)/30+44/45)
```

COMMENT: The iteration using the equation x=1.5cos(x) does not converge(The result does not show in here due to the infinite iteration). But the iteration using the equation x=cos(x)/30+44x/45 does converge. Actually, these two equations are equivalent.
x=cos(x)/30+44x/45
1350x=45cos(x)+1320x
30x=45cos(x)
x=1.5cos(x)
Part(c) can explain the behavior in part(a).

Page53_Exercise3

```{r}
twinprimes<-function(n) {
  if (n >=2) {
    sieve<-seq(2, n)
    primes<-c()
    for (i in seq(2, n)) {
      if (any(sieve==i)) {
        primes<-c(primes, i)
        sieve<-sieve[(sieve%%i)!=0]
      }
    }
    for (i in 2:length(primes)) {
      if (primes[i]-primes[i-1]==2)
        print(c(primes[i-1],primes[i])) 
      }
  } else {
    stop("Input value of n should be at least 2.")
    }
}
twinprimes(1000)
```

Page53_Exercise5

```{r}
mortgage<-function(n,P,open) {
  if (open==TRUE) {i=0.005}
  else {i=0.004}
  R<-(P*i)/(1-(1+i)^(-n))
  return(R)
}
mortgage(24,20000,TRUE)
```

Page55_Exercise4

```{r}
i1<-0
i2<-0.006
count<-0
while(abs(i2-i1)>0.000001){
  i1<-i2
  i2<-(1-(1+i1)^(-20))/19
  count<-count+1
}
i1
i2
count

i1<-0
i2<-0.95
count<-0
while(abs(i2-i1)>0.000001){
  i1<-i2
  i2<-(1-(1+i1)^(-20))/19
  count<-count+1
}
i1
i2
count
```

Page58_Exercise1

```{r}
curve(x^3+2*x^2-7,0,2)
x1<-0
x2<-2
count<-1
repeat {
  count<-count+1
  x3<-(x1+x2)/2
  f1<-x1^3+2*x1^2-7
  f2<-x1^3+2*x1^2-7
  f3<-x3^3+2*x3^2-7
  if (f3==0) break
  else {
    if (f3>0) {x2<-x3}
    else {x1<-x3}
  }
  if (abs(x2-x1)<0.000001) break
}
x1
f1
x2
f2
count
```

COMMENT: This bisection algorithm is based on the intermediate value theorem. The intermediate value theorem states that if f is continuous on a closed interval [a,b], and c is any number between  f(a) and f(b) inclusive, then there is at least one number x in the closed interval such that f(x)=c. It has a specializations: if a continuous function has values of opposite sign inside an interval, then it has a root in that interval.  

Page62_Exercise3

```{r}
bisection<-function(f,x1,x2) {
  repeat {
    x3<-(x1+x2)/2
    f1<-f(x1)
    f2<-f(x2)
    f3<-f(x3)
    if (f3==0) {
      print(x3)
      break
    } else {
      if (f1*f3>0) {x1<-x3}
      else {x2<-x3}
    }
    if (abs(x2-x1)<0.000001) {
      print((x1+x2)/2)
      break
    } 
  }
}
f<-function(x) x^3+2*x^2-7
bisection(f,0,2)
```
