---
title: "HW7"
output:
  pdf_document:
    fig_height: 3.5
---

Page86_Exercise4

```{r}
set.seed(19908)
U<-runif(1000)
##a
mean(U)
var(U)
sd(U)
```

COMMENT: If U~U(0,1),then E(U)=1/2, Var(U)=1/12=0.083333, SD(U)=(1/12)^0.5=0.288675.We can see the simulated average, variance, and standard deviation are close to the true values.

```{r}
##c
U60<-U[U<0.6]
prop60<-length(U60)/1000
prop60
punif(0.6)
```

COMMENT: 
Obviously, the simulated value is close to the theoretical value.

```{r}
##d
mean(1/(U+1))
##e
par(mfrow=c(1,2))
hist(U)
hist(1/(U+1))
```

Page91_Exercise3

```{r}
B<-rbinom(10000,18,0.76)
mean(B)
var(B)
```

COMMENT: If B~BIN(18,0.76),then E(U)=13.68, Var(U)=3.2832.We can see the simulated values are close to the theoretical values.

Page95_Exercise2

```{r}
R<-rpois(20,1.2)
R
```

Page99_Exercise3

```{r}
E<-rexp(10000,9)
mean(E)
var(E)
```

COMMENT: If E1~EXP(3) and E2~EXP(6),then E=min(E1,E2)~EXP(9).

Page101_Exercise3

```{r}
N<-rnorm(10000,3,4)
N<-N[abs(N)>2]
par(mfrow=c(1,2))
hist(N)
plot(density(N))
```

Page104_Exercise2

```{r}
x1<-runif(10000,0,3)
y1<-runif(10000)
mean(cos(x1-y1))*3
x2<-runif(10000,0,5)
y2<-runif(10000,0,2)
mean(exp(-(x2+y2)^2)*(x2+y2)^2)*10
```
